Fetch PMC Citation Info

### 2021-12-07 analysis_code/citation_fetching.Rmd
tidy6
one command execute

x <- read.table("data/PMC_2019-analysis.tsv",sep="\t",header=TRUE)
head(x)
PMCIDS <- unique(x$Pubmed.Central.ID)

@@

plot(df$Pubdate,df$NumCites)
mylm <- lm(df$NumCites ~ df$Pubdate)
abline(mylm,col="red")
summary(mylm)
cor.test(df$NumCites , as.numeric(df$Pubdate))
saveRDS(df,"cites_data.rds")

>>>>

x <- read.table("../data/PMC_2019-analysis.tsv",sep="\t",header=TRUE)
head(x)
PMCIDS <- unique(x$Pubmed.Central.ID)

@@

plot(df$Pubdate,df$NumCites)
mylm <- lm(df$NumCites ~ df$Pubdate)
abline(mylm,col="red")
summary(mylm)
cor.test(df$NumCites , as.numeric(df$Pubdate))
saveRDS(df,"../data/cites_data.rds")
